Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-06-03 supp/supp.qmd
Need to add more details on some analyses
Adding GLM analysis details

>>>>

## Data Analysis

#### Generational Analysis
To test whether a greater number of preprints were submitted by authors of earlier 'academic age', as quantified by the submitting authors first year of publication, we used a generalised linear model (GLM) with a negative binomial error distribution. We included the number of preprints submitted in a given year as the response variable and the first year of publication as the predictor variable. A negative, and significant, slope coefficient indicates support for researchers of earlier career stages submitting more preprints.
